---
geometry: margin=1in
linkcolor: darkmidnightblue
urlcolor: darkmidnightblue
fontawesome: yes
updated: yes
header-includes:
- \usepackage{etaremune} # used to number pubs backwards
- \usepackage[default]{sourcesanspro}
- \usepackage{fancyhdr} # to alter header and footer
- \pagestyle{fancy} 
- \fancyfoot[R]{`r format(Sys.time(), '%B %Y')`} # bottom right of page
- \fancyhead[R]{Emilio M. Bruna, p. \thepage} # top right of page
- \usepackage{setspace}
- \usepackage{parskip}
- \usepackage{xcolor}
- \AtBeginDocument{\let\maketitle\relax} # removes the standard Rmd title / date
# this changes the location and color of the sections, subsections, etc.
- \usepackage{sectsty} \sectionfont{\centering\color{darkmidnightblue}} # 
- \usepackage{sectsty} \subsubsectionfont{\color{darkmidnightblue}}
# define colors
- \definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
- \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
- \usepackage{xhfill} # used to make the line
output: pdf_document
# output: word_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE)
library(tidyverse)
library(gridExtra)
library(kableExtra)
# library(citr)
# library(RefManageR)
```
<!-- \begin{document}. -->

<!-- this next line suppresses the header (line, name,  page number) on 1st page -->
\thispagestyle{empty}  

# YOUR NAME
\vspace{-0.3cm}  <!--space between name and address -->
<!--\hfill moves all way to right -->
University of Florida\hfill email@ufl.edu  
Dept. of Metaphysics\hfill +1 (352) 867-5309  
PO Box 110430\hfill&nbsp;[www.your-web-site.org](www.your-web-site.org)  
Gainesville, FL 32611-1234 USA\hfill&nbsp;[\@YouTwitterOrGithub](https://twitter.com/you) 
\vspace{-0.5cm}  <!--there was too much space, so reduced it with minus: -Xcm -->

\par\noindent\rule{\textwidth}{0.4pt} <!-- makes the line   -->
<!-- \textbf{\textcolor{darkmidnightblue}{RESEARCH \& TEACHING INTERESTS:}} some, keywords, about, your research topics   -->

<!-- \textbf{\textcolor{darkmidnightblue}{LANGUAGES:}} Fluent in Spanish, English, Esperanto, and French   -->

\vspace{-0.6cm}  

<!-- ```{r, child=c('one.Rmd', 'two.Rmd')} -->
<!-- ``` -->

<!-- ```{r, child='one.Rmd'} -->
<!-- ``` -->

### EDUCATION
<!--to indent a block of stuff treat it as a 'group' and then set leftskip -->
<!--be sure to indicate where the group ends with \endgroup -->

\begingroup 
\setlength{\leftskip}{.2cm} 

<!-- ### EDUCATION \hrulefill\ -->
<!-- TEXT \hrulefill\ -->
<!-- Here is some text\xfill{1pt} \par -->
<!-- Here is some text\xfill{8pt} \par -->
<!-- Here is some text\xhrulefill{darkmidnightblue}{2pt}\par -->
<!-- Here is some text\xhrulefill{darkmidnightblue}{1ex}\par -->
<!-- HOW TO MAKE LINE COLOR SAME'? -->
<!-- https://tex.stackexchange.com/questions/32597/vertically-centered-horizontal-rule-filling-the-rest-of-a-line -->
<!-- \textbf{\textcolor{darkmidnightblue}{EDUCATION }}\xrfill[0.5ex]{0.5pt} -->

<!-- ### EDUCATION \hrulefill -->



2001\hspace{4mm} Ph.D. in Biology, University of Mars  
<!-- &nbsp;&nbsp;&nbsp;&nbsp;\hspace{6mm}  _Dissertation Advisor: Person Name_   -->
1995\hspace{4mm} M.S. in Biology, University of Venus  
<!-- &nbsp;&nbsp;&nbsp;&nbsp;\hspace{6mm} _Thesis Advisor: Person Name_   -->
1994\hspace{4mm} B.S. in Evolution, University of California 

\endgroup 

### PROFESSIONAL APPOINTMENTS
\begingroup 
\setlength{\leftskip}{.2cm} 

2020-Present\hspace{6mm}**Professor**, University of California  
&nbsp;\hspace{24mm}Department of Wildlife Ecology

2018-2020\hspace{10mm}**President**, Student Group 

2017-2018\hspace{10mm}**Treasurer**, Student Group

\endgroup


\vspace{-0.2cm}
### FELLOWSHIPS AND AWARDS

\begingroup 
\setlength{\leftskip}{.2cm} 
2022\hspace{4mm}Graduate Fellowship, University of Florida  
2020\hspace{4mm}Best Presentation, Ecological Society of Mexico  
2020\hspace{4mm}Outstanding Teaching Assistant, UF College of Agricultural and Life   Sciences    

\endgroup


### RESEARCH GRANTS    

\begingroup 
\setlength{\leftskip}{.2cm}  

1. MH Foundaiton. 'Support for the Study of bugs' ($100,000, 2022-2023)

1. MNGA Foundation. 'Bugs are great' ($74,060, 2020-2021)

\endgroup

### PUBLICATIONS  

1. Squire, K. (2011). Video games and learning: Teaching and participatory culture in the digital age. Teachers College Press. 

2. Wang, Q., Chen, W., & Liang, Y. (2017). Effects of inquiry-based learning supported by mobile technology on students’ learning achievements and attitudes. Journal of Educational Technology Development and Exchange, 8(1), 1-20. 

3. Wong, L. H., Chai, C. S., & Tan, E. (2016). Virtual laboratories in science education: A review of the literature. Journal of Educational Technology Development and Exchange, 9(1), 1-19. 

<!-- ### SOFTWARE  -->

<!-- ### OTHER WRITING & SCHOLARLY COMMUNICATION -->

<!-- ### PUBLICLY ARCHIVED DATASETS & CODE  -->

<!-- ### MANUSCRIPTS IN PREPARATION  -->

### TEACHING EXPERIENCE
\begingroup 
\setlength{\leftskip}{.2cm}  
Guest Lecture, The Future of Rain Forests (Undergraduate, 2022)  
Instructor, Data Collection & Field Methods (Graduate, 2019)  

\endgroup 

### GRADUATE STUDENTS ADVISED

```{r GradStudents, echo=FALSE,message = FALSE,warning=FALSE}
grad_advised<-read_csv("./cv_files/grad_advised.csv") %>% filter(role=="advisor") %>% select(-role)
kbl(grad_advised,digits = 1,
                  format = "latex",
                  align="l",
    col.names = NULL,
    longtable = T,
                  row.names = FALSE,
                  booktabs=T,
                  linesep = "") %>%
  kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down"),
                full_width = F,
                font_size = 10,
                position = "left") %>%
  sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .)
```

### DOCTORAL STUDENT COMMITTEE SERVICE

```{r DocCmte, echo=FALSE,message = FALSE,warning=FALSE}
grad_advised<-read_csv("./cv_files/grad_advised.csv") %>% filter(role=="doc_cmte") %>% select(-role)
kbl(grad_advised,digits = 1,
                  format = "latex",
                  align="l",
                  col.names = NULL,
                  row.names = FALSE,
                  booktabs=T,
                  longtable = T, 
                  linesep = "") %>%
  kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down"),
                full_width = F,
                font_size = 10,
                position = "left") %>%
  sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .)
```

### MASTERS STUDENT COMMITTEE SERVICE
```{r MastersCmte, echo=FALSE,message = FALSE,warning=FALSE}
grad_advised<-read_csv("./cv_files/grad_advised.csv") %>% filter(role=="masters_cmte") %>% select(-role)
kbl(grad_advised,digits = 1,
                  format = "latex",
                  align="l",
        longtable = T, 
    col.names = NULL,
                  row.names = FALSE,
                  booktabs=T,
                  linesep = "") %>%
  kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down"),
                full_width = F,
                font_size = 10,
                position = "left") %>%
  sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .)
```

### SERVICE

\begingroup 
\setlength{\leftskip}{.2cm}
Search Committee, UF QUEST Program (2023)  
Samuel P. Harn Museum of Art Faculty Council (2012-2015)   
Selection Committee, UF Undergraduate Faculty Mentor/Advisor of the Year (2022)    

__Referee for journals (No. of reviews):__ 
\setlength{\leftskip}{.2cm}  

*Trends in Ecology and Evolution* (1)   
*Nature Human Behavior* (1)  
*Nature Ecology & Evolution* (2)  

\endgroup 

### PRESENTATIONS
```{r talks, echo=FALSE,message = FALSE,warning=FALSE}
talks<-read_csv("./cv_files/talks.csv", col_types = cols(.default = "c")) %>% 
  select(-year)  %>% 
  replace_na(list(year2=""))
kbl(talks, 
      format    = "latex", 
      align = "l",
      longtable = T, 
      row.names = FALSE,
      col.names = NULL,
      booktabs=T,
      linesep = "") %>%
  kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down"),
                full_width = F,
                font_size = 10,
                position = "left") %>%
  sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .)
```

<!-- ### INTERVIEWS & MEDIA APPEARANCES   -->
<!-- \begingroup  -->
<!-- \setlength{\leftskip}{.2cm}   -->

<!-- 2013\hspace{4mm} Item   -->
<!-- 2013\hspace{4mm} Item   -->

<!-- \endgroup -->

<!-- ### PROFESSIONAL DEVELOPMENT   -->
<!-- \begingroup  -->
<!-- \setlength{\leftskip}{.2cm}   -->

<!-- 2013\hspace{4mm} Item   -->
<!-- 2013\hspace{4mm} Item   -->

<!-- \endgroup -->

<!-- ### MEMBERSHIPS IN PROFESSIONAL SOCIETIES   -->

<!-- \begingroup  -->
<!-- \setlength{\leftskip}{.2cm}   -->

<!-- Ecological Society of America   -->
<!-- Association for Tropical Biology and Conservation   -->

<!-- \endgroup -->
